### 2018-08-07 paper/design.tex
New overview figure (Fig 1). Caption still to be added.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline_figure_only.pdf_tex}
  \caption{\label{fig:outline}%
    %\commentDaniel{We must adapt this figure to the text.}%
    Outline of \name's components. Users' squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them with random peers (\cref{ssec:device_availability}); using the two 
    overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
    These protocols enable secure file transfer between users 
    (\cref{ssec:por}).}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  %  \import{figures/}{outline_figure_only.pdf_tex}
    \includegraphics[width=\columnwidth]{figures/OverviewSPORES_cropped}
  \caption{\label{fig:outline}%
    %\commentDaniel{We must adapt this figure to the text.}%
    %% Outline of \name's components. Users' squads of devices are circled in gray. 
    %% From top to bottom: a user's devices collaborate through the Squad Overlay 
    %% (\cref{sec:squad_overlay}); online devices globally share information about 
    %% them with random peers (\cref{ssec:device_availability}); using the two 
    %% overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
    %% These protocols enable secure file transfer between users 
    %% (\cref{ssec:por}).
    \protect\commentFT{TODO by Francois: describe figure}}
\end{figure}
